I would like to thank Prof. Madicken Munk, who mentored me as a newly minted
graduate student and who inspires constantly to think big and find the impact
in my work. Relatedly, I would like to thank Prof. Kathryn Huff, who has been a
mentor to me at every step of my collegiate education and who has
showed me how to be a happy warrior.

I would like to thank my fellow graduate students and the members of
\gls{arfc}; particularly Amanda Bachmann, Sam Dotson, Nataly Panczyk, Olek
Yardas, Zo\"{e} Richter, Gwendolyn Chee, Sun Myung Park, Rhys MacMillian,
and Ceser Zambrano. I would like to especially thank Luke Siefert for his
assistance running the Serpent simulations that were used in this work.

Throughout the years, I learned much from my group mates, advisors, and
mentors, but I would be remiss to not acknowledge that I went to the school of
open source and learned much from countless developers who work openly to
better science. In particular the \cyclus community, especially Prof. Paul P.H.
Wilson, Katie Mummah, Jin Whan Bae, and Dr. Eva Davidson.

I owe many thanks to my parents, brother, grandparents, family, partner, and
friends who have reminded me---sometimes to my chagrin---that life keeps going
outside the walls of my office. To my cousin Matthew, I can not wait to explain
this part of my life to you someday when we are reunited because I know you are
going to have questions.

This research was performed, in part, using funding received from the DOE
Office of Nuclear Energy's Nuclear Energy University Program (Project 23-29656
DE-NE0009390) 'Illuminating Emerging Supply Chain and Waste Management
Challenges'.

This research was supported in part by an appointment to the Oak Ridge National
Laboratory Research Student Internships Program, sponsored by the U.S.
Department of Energy and administered by the Oak Ridge Institute for Science
and Education.